**Density Dependence**

### 2022-12-16 Rmd/runDD.Rmd
plot

```{r}
plot(qmax((biomass(eq)%/%biomass(eq)[,c(14)])^0.3,0.5))+
  scale_y_continuous(labels = scales::percent)+
  xlab("Biomass")+ylab("% Change in mass-at-age")
```

**Figure `r iFig=iFig+1; iFig`** Density dependence multiplier

@@

ggplot(as.data.frame(wt))+           
    geom_line(aes(age,data,col=factor(year)))+
    theme(legend.position="none")+
    scale_x_continuous(limits=c(0,15))+
    xlab("Age")+ylab("NMass-at-age")
```

>>>>

```{r}
plot(qmax((biomass(eq)%/%biomass(eq)[,c(14)])^0.3,0.5))+
  scale_y_continuous(labels = scales::percent)+
  geom_vline(aes(xintercept=14),col="red")+
  xlab("Biomass")+ylab("% Change in mass-at-age")
```

**Figure `r iFig=iFig+1; iFig`** Density dependence multiplier, red is $B_{MSY}$

@@

ggplot(as.data.frame(wt))+           
    geom_line(aes(age,data,col=factor(year)))+
    theme(legend.position="none")+
    scale_x_continuous(limits=c(0,15))+
    xlab("Age")+ylab("Mass-at-age")
```
